---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CMORprojects

<!-- badges: start -->
<!-- badges: end -->

The goal of CMORprojects is to provide tools to optimise a research project data analysis workflow for research projects undertaken at CMOR.

## Installation

You can install the latest version of CMORprojects from [GitHub](https://github.com) with:

``` r
install.packages("remotes")
remotes::install_github("uo-cmor/CMORprojects")
```

## Functions

Create a new research project folder:

```{r create-project}
# create_research_project("~/path/to/project/folder")
```

Create a target to render RMarkdown report to docx file in a `targets` pipeline:

```{r render_manuscript}
# targets <- list(
#   tar_file(data_file, "raw_data/data.csv"),
# 	tar_target(data, read_raw_data(data_file)),
# 	tar_target(analysis, do_some_analysis(data)),
#   tar_file(file_word_styles, "output/word-styles-reference-01.docx"),
#   tar_file(file_csl, "output/vancouver.csl"),
#   tar_file(file_bib, "output/references.bib"),
# 	tar_render_manuscript(manuscript, "output/manuscript.Rmd", "output/manuscript.docx",
#                         file_word_styles, file_csl, file_bib)
# )
```
